Time invariant analysis of epidemics with \pkg{EpiCompare}

### 2020-12-20 jss/EpiCompare-paper/EpiCompare-paper.Rmd
distance functions now can return a tidy_dist_mat object

```{r}
dmat <- compression_df %>% 
  dist_matrix_innersq_direction(
    position = c(1:length(compression_df))[
      names(compression_df) %in% c("S","I", "R")],
    id_as_columns = T)

tdmat <- tidy_dist_mat(as.matrix(dmat[,-c(1:2)]),
                       rownames_df = ungroup(dmat[,1:2]),
                       colnames_df = ungroup(dmat[,1:2]))

@@

dmat <- compression_df %>% 
  dist_matrix_innersq_direction(
    position = c(1:length(compression_df))[
      names(compression_df) %in% c("S","I", "R")],
    id_as_columns = T)

tdmat <- tidy_dist_mat(as.matrix(dmat[,-c(1:2)]),
                       rownames_df = ungroup(dmat[,1:2]),
                       colnames_df = ungroup(dmat[,1:2]))

>>>>

```{r}
tdmat <- compression_df %>% 
  dist_matrix_innersq_direction(
    position = c(1:length(compression_df))[
      names(compression_df) %in% c("S","I", "R")],
    tdm_out = T)

@@

tdmat <- compression_df %>% 
  dist_matrix_innersq_direction(
    position = c(1:length(compression_df))[
      names(compression_df) %in% c("S","I", "R")],
    tdm_out = T)

### 2020-12-20 jss/EpiCompare-paper/EpiCompare-paper.tex
distance functions now can return a tidy_dist_mat object

\begin{CodeChunk}
\begin{CodeInput}
R> dmat <- compression_df %>% 
+   dist_matrix_innersq_direction(
+     position = c(1:length(compression_df))[
+       names(compression_df) %in% c("S","I", "R")],
+     id_as_columns = T)
R> 
R> tdmat <- tidy_dist_mat(as.matrix(dmat[,-c(1:2)]),
+                        rownames_df = ungroup(dmat[,1:2]),
+                        colnames_df = ungroup(dmat[,1:2])) 
R> 
R> 
R> simple_sir_true_obs_info <- tdmat %>% 
+   compare_new_to_rest_via_distance(
+     new_name_id = data.frame(Type = "true observation", sim = 0),
+     distance_func = distance_psuedo_density_function, 
+     sigma = "20%") 
\end{CodeInput}
\end{CodeChunk}

>>>>

\begin{CodeChunk}
\begin{CodeInput}
R> tdmat <- compression_df %>% 
+   dist_matrix_innersq_direction(
+     position = c(1:length(compression_df))[
+       names(compression_df) %in% c("S","I", "R")],
+     tdm_out = T)
R> 
R> simple_sir_true_obs_info <- tdmat %>% 
+   compare_new_to_rest_via_distance(
+     new_name_id = data.frame(Type = "true observation", sim = 0),
+     distance_func = distance_psuedo_density_function, 
+     sigma = "20%") 
\end{CodeInput}
\end{CodeChunk}
